---
title: "Brand Map"
author: "Weishan He"
output: html_document
---

```{r setup, include=FALSE}
library(readxl)
library(glmnet)
library(dplyr)
library(boot)
```

### 1. Build brand maps for car brands. The client's brand is Infinity
```{r}
## Reading the data
cars_data <- read_excel("Cars_Data.xlsx", sheet = "Infinity Data")
head(cars_data)

## Getting x and y
cars_y <- cars_data$`Overall Preference`
cars_x <- as.matrix(cars_data[,2:16])

## Creating cor matrix
cars_cor <- cor(cars_x)

##### Principal Components Analysis #####
cars_out1 <-  eigen(cars_cor)	    # eigen decomposition of correlation matrix
cars_va <-  cars_out1$values			# eigenvalues
cars_ve <-  cars_out1$vectors		  # eigenvector

##### Ploting eigenvalues per number of components #####
plot(cars_va, ylab = "Eigenvalues", xlab = "Component Nos")				# screen plot
```

### 2. How many factors to retain?
```{r}
## Selecting factors to retain (eigenvalues > 1)
cars_ego <- cars_va[cars_va > 1]							# eigenvalues > 1
cars_nn <- nrow(as.matrix(cars_ego))					# number of factors to retain
cars_nn 

#Answer: Retain 4 factors
```

### 3. Assign names to the retained factors (you may need to flip the factors and then assign names)
```{r}
# Eigenvectors associated with the retained factors
cars_out2 <- cars_ve[,1:cars_nn]			
cars_out3 <- ifelse(abs(cars_out2) < 0.3, 0, cars_out2)		# ignore small values < 0.3

rownames(cars_out3) <- c("Attractive", "Quiet", "Unreliable", "Poorly Built", "Interesting", "Sporty", "Uncomfortable", "Roomy", "Easy Service", "Prestige", "Common", "Economical", "Successful", "AvantGarde", "Poor Value")
cars_out3

# Naming the columns
column_names = c('Premium', 'Convenience','Economical', 'Innovative')
colnames(cars_out3) <- column_names
cars_out3

#The names assigned to the benefit factors are: Premium, Convenience, Economical and Innovative.

# flip the eigenvectors b/c later we will see that regression betas are negative. We flip the eignevector so that the slopes become positive for naming the four benefits

# Assign names based on the rownames and signs of coefficients
cars_out4 = (-1) * cars_out3[,1:2]	
cars_out4 <- cbind(cars_out4, cars_out3[,3:4])
cars_out4

# Principal Componenent "Scores" are the linear combination of original variables, where the weights come from the eigenvectors.
# Denoted by Z in the slides
cars_z <- cars_x %*% cars_out4			# Component Scores; coordinates of the brands in the map
rownames(cars_z) <- cars_data$Brands
cars_z

cars_out5 = lm(cars_y ~ cars_z)		# Preference Regression to estimate how benefits drive overall preferences = f(benefits)

summary(cars_out5)

## NOTE: you want all the slopes to be positive. If negative, then flip those Z variables by multiplying by -1. 
```

```{r}
##### Iso Preference Line and Ideal Vector ####			

## Significant Benefit Factors: Z1 and Z3

## Let z3 be the y-axis and z1 as the x-axis	
## Plot (z3, z1) to get brands in factor space of benefit 1 and benefit 3 

# coordinates of brands in (z1, z3) space
cars_Z1 = cars_z[,1]
cars_Z3 = cars_z[,3]
cars_z.out = cbind(cars_Z1, cars_Z3)
rownames(cars_z.out) = cars_data$Brands
cars_z.out

# Brand Map in Z1-Z3 space. Plot, add labels  ## Need to run the whole chunk to work
plot.new()
plot(cars_Z1, cars_Z3, main = "Brands in Z1(Premium) and Z2(Economical) space", xlab = "Premium", ylab = "Economical", col = "lightblue", pch = 16, cex = 1) +
  text(cars_z.out, labels = row.names(cars_z.out), font = 0.5, cex = 0.5, pos = 4)	# labeling brands					

```

### 4. Explain iso-preference line and its difference from the regression line
The iso-preference line is composed of offers that are equally preferred by customers - along the line, customers are indifferent between the combinations of factors. Offers to the right are more preferred by customers whereas offers to the left are less preferred. On the other hand, the regression line in our case estimates the “overall preference” score based on the different benefits/factors. Each point in the regression line corresponds to the estimated dependent variable value based on collective independent variables.

### 5. Explain what is an ideal vector and why it indicates the direction of increasing preferences 
An ideal vector is the vector to find the importance weights of the evaluation dimensions on the preference. This is perpendicular to the iso-preference lines mentioned above, representing the direction of increasing preferences. When we create a perceptual map to show the consumer’s understanding of the positions of competing brands, the estimated coefficients from the attributes are required to build the axes on the map. The ratio of these two preferences becomes the slope of the ideal vector. With the direction of the vector towards the northeast, it shows us which brand should improve the product design.

### 6. Compute the angles of iso-preference line and ideal vector arrow
```{r}
# Slopes of iso-preference and ideal vector	
cars_b1 = as.vector(coef(cars_out5)[2])
cars_b3 = as.vector(coef(cars_out5)[4])
cars_slope.iso.preference = - cars_b1/cars_b3						
cars_slope.ideal.vector = cars_b3/cars_b1 						

# Angles of iso-preference and ideal vector	
cars_angle.iso.preference = atan(cars_slope.iso.preference)*180/pi	# -56.20927
cars_angle.ideal.vector = atan(cars_slope.ideal.vector)*180/pi # 33.79073

#Answer: The angles of the iso-preference line is -56.20927 degree and that of the ideal vector arrow is 33.79073 degree.
```

### 7. Find 95% confidence interval for the angle of the ideal vector. Use data bootstrap method we learnt in Class 3.
```{r}
nn <- nrow(cars_data)
cars_yhat <- predict(cars_out5)
rr <- cars_out5$resid						# residuals based on original data, to be used for resampling
bb <- 1000							# number of resampling

# Do Residual Bootstrap 1000 times to get 95% CI for cars_angle.ideal.vector.out
cars_angle.ideal.vector.out <- matrix(0, bb, 1 )
set.seed(123)
for(ii in 1:bb) {
  cars_ystar <- cars_yhat + rr[sample(nn, nn, replace = TRUE)]		# y* with original yhat plus r*
  cars_out5.star = lm(cars_ystar ~ cars_z)	# lm with new y* and same cars_z to get new b1hat* and b3hat*
  
  # Slope of ideal vector	
  cars_b1 = as.vector(coef(cars_out5.star)[2])
  cars_b3 = as.vector(coef(cars_out5.star)[4])
  cars_slope.ideal.vector = cars_b3/cars_b1 	
  
  # Angle of ideal vector	
  cars_angle.ideal.vector.out[ii,] = atan(cars_slope.ideal.vector)*180/pi # 33.79073
}

CI_lower <- quantile(cars_angle.ideal.vector.out, probs = 0.025) # 22.14003
CI_upper <- quantile(cars_angle.ideal.vector.out, probs = 0.975) # 44.85088

#Answer: The 95% confidence interval for the angle of the ideal vector is (22.14003, 44.85088).
```

### 8. Recommend to Infinity's managers what they should do to improve their product design
Given the brand map that includes Z1 and Z3, the dimensions that turned out to be significant, it is quite evident that based on Z1, the premium benefit, that Infinity is already differentiated to some extent in terms of their premium-ness as they are the most preferred as a premium brand.The brand has received a negative score for Z3, the economical benefit and that aligns with the fact that the brand is indeed recognized as the most preferred premium brand.

Therefore, we would advise them to solidify their premium image through their product design. Infinity could focus on features and details that denotes1) attractive 2) quiet 3) prestage and 4) successful image of the brand. Not only that, they should stay away from designs that are associated with poorly built images.

The biggest competitor to Infinity is BMW as BMW is in the closest proximity to Infinity. Therefore, our goal being to be a differentiated and distinctive brand in the market, Infinity should stay from neighboring brands. To be specific, we’d recommend them to look out for new models and new design features that BMW is coming up with and see if those could bring BMW’s position closer to Infinity’s, which then becomes a bigger threat. Also, to solidify their brand positioning, Infinity should continue to focus on the premium aspect of the brand and design and try to go farther on the horizontal axis to further differentiate themselves in the premium field and thereby avoid competition.